---
title: "Preliminary Analysis of Prey "Aggregation""
author: "Elan Portner, Jessie Perelman, Melanie Abecassis, Anela Choy"
date: "1/8/2018"
output: html_document
---

#Size distribution of specimens
###for which stomachs have been dissected

```{r get necessary packages, include=FALSE}
### Clear workspace ###
rm(list = ls(all = TRUE)); 

### load necessary packages (install packages before first use by un-commenting install.packages function. Comment out install functions after first run) ###

# install.packages("marmap")
# install.packages("mapplots")
# install.packages("RColorBrewer")
# install.packages("ggplot2")

library(marmap)
library(mapplots)
library(RColorBrewer)
library(ggplot2)

```


```{r load data files, echo=FALSE}
### Load necessary data files ###

## Specimen metadata is spread across several data files

loc <- read.csv("ALEP_NOAA_SPECIMEN_07-2016.csv")
prey <- read.csv("ALEP_PREY_07-2016.csv")
len = (read.csv("ALEP_SPECIMEN_LOG_07-2016.csv")[,c(1,3)])
## fg <- read.csv("preyfg.csv")
ind <- read.csv("ALEP_PREY_INDIV_07-2016.csv")

## family <- read.csv("preytable_041616.csv")
full <- read.csv("ALEP_PRED_SUMM_07-2016.csv")
taxon = (read.csv("ALEP_TAXONOMIC_IDs_07-2016.csv")[,c(1,10)])
types = unique((types <- read.csv("preytypes3_09-2016.csv")[,c(1,3)]))
func = read.csv("functionalgroups_09-14-2016.csv")[,c(1:3)]


```

#Temporal distribution of specimens
###for which stomachs have been dissected

```{r}

```


```{r, echo=FALSE}

```

#Spatial distribution of specimens
###for which stomachs have been dissected and location data acquired

```{r}

```


```{r, echo=FALSE}

```

#Spatial distribution of prey by numerical density
###for which stomachs have been dissected and location data acquired

```{r}

```


```{r, echo=FALSE}

```

